Restructuring Spoken Corpus for Streaming Emulation

### 2020-07-03 2020-fedcsis-sofia-denoise/denoise.tex
add fedcsis denoise and splits papers

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Speech Enhancement for Low Quality Audio}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Oldřich Krůza\inst{1}\orcidID{0000-0002-7510-6470}\\
\and David Klusáček\inst{1}\orcidID{0000-0002-0144-2092}}
%
\authorrunning{Krůza \and Klusáček}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
\email{\{kruza,klusacek\}@ufal.mff.cuni.cz}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper presents an attempt to solve the problem of bad audio quality
affecting the listening experience and accuracy of speech-to-text systems. We
describe two experiments: one with automated spectral subtraction and one
with Gycle-GAN domain transfer from the defect to the
pure as a way to reduce the impact of noise, overdrive, reverberation and other
defects.
\keywords{speech recognition, GycleGAN, domain transfer, signal processing}
\end{abstract}

@@

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
WER    & original model & denoised model \\
\hline
original testing data & 0.189 & 0.940 \\
denoised testing data & 0.698 & 0.941 \\
\hline
\end{tabular}
\caption{Word error rate for the original and denoised test data by a model trained
on the original and denoised training data.}\label{tab:results-denoise}
\end{center}
\end{table}

@@

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
           & original & transferred \\
\hline
overdriven & 0.450 & 0.441 \\
low-speed  & 0.685 & 0.939 \\
\hline
\end{tabular}
\caption{Word error rate for the two damaged clusters before and after CycleGAN
transfer.}\label{tab:results}
\end{center}
\end{table}

@@

\begin{figure}[htpb]
\includegraphics[scale=0.4]{rc/plzen.eps}
\caption{Wave form (above) and spectrogram (below) of a recording taken in low
tape speed before the CycleGAN transfer (left) and afterwards (right).}
\label{fig:plzen}
\end{figure}

\begin{figure}[htpb]
\includegraphics[scale=0.4]{rc/overdrive.eps}
\caption{Wave form (above) and spectrogram (below) of an overdriven recording
before the CycleGAN transfer (left) and afterwards (right).}
\label{fig:overdrive}
\end{figure}

>>>>

% This file demonstrates how to use the IEEEConf LaTeX2e macro package,
% to prepare a manuscript for proceedings on CD of the conference
% FedCSIS
%
\documentclass[conference]{IEEEtran}
%\documentclass[a4paper]{IEEEconf}

% This package serves to balance the column lengths on the last page of the document.
% please, insert \balance command in the left column of the last page
\usepackage{balance}

%% to enable \thank command
\IEEEoverridecommandlockouts 
%% The usage of the following packages is recommended
%% to insert graphics
\usepackage[dvips]{graphicx}
% to typeset algorithms
% to typeset code fragments
\usepackage{listings}
% provides various features to facilitate writing math formulas and to improve the typographical quality of their output.
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
% por urls typesetting and breaking
\usepackage{url}
% for vertical merging table cells
\usepackage{multirow}
\usepackage{flushend}

% define environments for remarks and examples
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

%
%
\title{Speech Enhancement for Low Quality Audio}
%
%
\author{
\IEEEauthorblockN{Jan Oldřich Krůza, David Klusáček}
\IEEEauthorblockA{
Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
Email: \{kruza,klusacek\}@ufal.mff.cuni.cz}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

\begin{document}
\maketitle              % typeset the title of the contribution

\begin{abstract}
The paper presents an attempt to solve the problem of bad audio quality
affecting the listening experience and accuracy of speech-to-text systems. We
describe two experiments: one with automated spectral subtraction and one
with Gycle-GAN domain transfer from the defect to the
pure as a way to reduce the impact of noise, overdrive, reverberation and other
defects.
\end{abstract}

@@

\begin{table}[htpb]
\caption{Word error rate for the original and denoised test data by a model trained
on the original and denoised training data.}\label{tab:results-denoise}
\centering
\begin{tabular}{|l||r|r|}
\hline
WER    & original model & denoised model \\
\hline
original testing data & 0.189 & 0.940 \\
denoised testing data & 0.698 & 0.941 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[htpb]
\caption{Word error rate for the two damaged clusters before and after CycleGAN
transfer.}\label{tab:results}
\centering
\begin{tabular}{|l||r|r|}
\hline
           & original & transferred \\
\hline
overdriven & 0.450 & 0.441 \\
low-speed  & 0.685 & 0.939 \\
\hline
\end{tabular}
\end{table}

@@

\begin{figure*}[tpb]
\centering
\includegraphics[width=0.9\hsize]{rc/plzen.eps}
\caption{Wave form (above) and spectrogram (below) of a recording taken in low
tape speed before the CycleGAN transfer (left) and afterwards (right).}
\label{fig:plzen}
\end{figure*}

\begin{figure*}[tpb]
\centering
\includegraphics[width=0.9\hsize]{rc/overdrive.eps}
\caption{Wave form (above) and spectrogram (below) of an overdriven recording
before the CycleGAN transfer (left) and afterwards (right).}
\label{fig:overdrive}
\end{figure*}

### 2020-07-03 2020-fedcsis-sofia-restructuring/splits.tex
add fedcsis denoise and splits papers

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Restructuring Spoken Corpus for Streaming Emulation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Oldřich Krůza\inst{1}\orcidID{0000-0002-7510-6470}}
%
\authorrunning{Jan Krůza}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
\email{kruza@ufal.mff.cuni.cz}}
%
\maketitle              % typeset the header of the contribution
%

@@

The corpus arose as a set of amateur recordings on magnetic tapes. The author of
the talks, Mr. Karel Makoň\cite{hajek2007cesky}, a Czech mystic, started giving talks in private
groups after his deportation into a concentration camp in 1939, and stopped in
1991, two years before his death. His regular listeners were recording his
talks. I don't know exactly when the recording started but the earliest denoted
year is 1973. The earliest year I could make out from analyzing the contents is
1970 on an undated recording.

@@

There is also a three-hour video on youtube: \\
\texttt{https://www.youtube.com/watch?v=UaNm9jnnJiA}

@@

Option 4 - waiting for streaming support in Web Audio API might seem silly but the issue has been discussed by the Web Audio API developer team, see https://github.com/WebAudio/web-audio-api/issues/1305 .

@@

The corpus can be accessed through its web interface at
\texttt{http://radio.makon.cz/}. The playback and other operations like playing
back or downloading an arbitrary span (which can span a segment boundary) can be
tested there. The source code for splitting the audio can be accessed at
GitHub: \\
\texttt{https://github.com/Sixtease/CorpusMakoni/tree/master/scripts}.
Similarly, the source code for the JavaScript part that works with the segments
can be found at its GitHub repository:
\texttt{https://github.com/Sixtease/MakonReact}, specifically in the files
\texttt{src/store/audio.js} and \texttt{src/store/AudioChunks.js}.

>>>>

% This file demonstrates how to use the IEEEConf LaTeX2e macro package,
% to prepare a manuscript for proceedings on CD of the conference
% FedCSIS
%
\documentclass[conference]{IEEEtran}
%\documentclass[a4paper]{IEEEconf}

% This package serves to balance the column lengths on the last page of the document.
% please, insert \balance command in the left column of the last page
\usepackage{balance}

%% to enable \thank command
\IEEEoverridecommandlockouts 
%% The usage of the following packages is recommended
%% to insert graphics
\usepackage[dvips]{graphicx}
% to typeset algorithms
% to typeset code fragments
\usepackage{listings}
% provides various features to facilitate writing math formulas and to improve the typographical quality of their output.
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
% por urls typesetting and breaking
\usepackage{url}
% for vertical merging table cells
\usepackage{multirow}
\usepackage{flushend}

% define environments for remarks and examples
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

%
%
\title{Restructuring Spoken Corpus for Streaming Emulation}
%
%
\author{
\IEEEauthorblockN{Jan Oldřich Krůza}
\IEEEauthorblockA{
Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
Email: kruza@ufal.mff.cuni.cz}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

\begin{document}
\maketitle              % typeset the title of the contribution

@@

The corpus arose as a set of amateur recordings on magnetic tapes. The author of
the talks, Mr. Karel Makoň\cite{hajek2007cesky}, a Czech mystic, started giving talks in private
groups after his deportation into a concentration camp in 1939, and ceased in
1992, one year before his death. His regular listeners were recording his
talks. I don't know exactly when the recording started but the earliest denoted
year is 1973. The earliest year I could make out from analyzing the contents is
1970 on an undated recording.

@@

There is also a three-hour video on youtube: \\
\url{https://www.youtube.com/watch?v=UaNm9jnnJiA}

@@

Option 4 - waiting for streaming support in Web Audio API might seem silly but
the issue has been discussed by the Web Audio API developer team, see
\url{https://github.com/WebAudio/web-audio-api/issues/1305}.

@@

The corpus can be accessed through its web interface at
\url{http://radio.makon.cz/}. The playback and other operations like playing
back or downloading an arbitrary span (which can span a segment boundary) can be
tested there. The source code for splitting the audio can be accessed at
GitHub: \\
\url{https://github.com/Sixtease/CorpusMakoni/tree/master/scripts}.
Similarly, the source code for the JavaScript part that works with the segments
can be found at its GitHub repository:
\url{https://github.com/Sixtease/MakonReact}, specifically in the files
\url{src/store/audio.js} and \url{src/store/AudioChunks.js}.
